Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-06-12 revisionMemo/rev1.tex
add graphs

\end{enumerate}

>>>>

		\begin{figure}
			\centering
			\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
			\label{fig:ameBias}
			\includegraphics[width=1\textwidth]{ameSimBias_all_asaProbit.pdf} \\
		\end{figure}

		\begin{figure}
			\centering
			\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
			\label{fig:ameBias}
			\includegraphics[width=1\textwidth]{ameSimBias_all_asa.pdf} \\
		\end{figure}

		\begin{figure}
			\centering
			\caption{Proportion of times the true value fell within the estimated 95\% confidence interval for the standard, AME, and oracle models from 1,000 simulations.}
			\label{fig:ameCalib}
			\includegraphics[width=1\textwidth]{ameSimCover_all_asaProbit.pdf} \\
		\end{figure}

		\begin{figure}
			\centering
			\caption{Proportion of times the true value fell within the estimated 95\% confidence interval for the standard, AME, and oracle models from 1,000 simulations.}
			\label{fig:ameCalib}
			\includegraphics[width=1\textwidth]{ameSimCover_all_asa.pdf} \\
		\end{figure}		
		}}
	\end{itemize}
\end{enumerate}

### 2020-06-12 revisionMemo/rev2.tex
additional sim cases
add graphs

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
		We thank the reviewer for their comments and suggestions.
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
			The reviewer raises an important connection to the spatial literature. The types of geographic dependencies in international relations are generally monadic in nature -- civil war spreads from Rwanda to Uganda, or protest from Lebanon to Syria. With dyadic data, however, we cannot use the common geographic adjacency matrices used for normal spatial econometrics, because in dyadic data a W matrix would need to specify how dyad i,j relates to dyad k,l (for every i,j,k,l). In the simulation, we do not include a spatial lag model because this would require specifying a spatial dependence pattern (see Plumper and Neumayer 2010 for a more in-depth discuss on spatial lags). \textbf{CD}: I added this as a footnote on p.9. I moved this footnote around a LOT but I think it needs to live somewhere in the simulation. It felt awkward within the text.
%		CDMG: Flag for discussion. We brainstormed how to fit this into the simulation, but wouldn't simulating a W matrix be a bit arbitrary here?
%		Reference papers that have thought about what happens when we get the wrong W
%		general gist .. spatial models of dyadic dvs are great if we know how to characterize the diffusion amtrices, but the point of our approach is that we may not know how to actually characterize the ways in which actors are related to one another on some diffusion space.
%		reference franzesse et al mstar framework as a way to operationalize multiple pathways of diffusion in a spatial econometric approach
	\item It would help if the author discussed in more depth the properties of the AME estimator in the presence of unobserved dependencies. One would imagine that the oracle model, where all the unobserved factors and dependencies are accounted for should always outperform a parametric or semi-parametric estimator. Relatedly, it also would help to have a more technical discussion of the properties of AME models, particularly in terms of the bias-variance trade off.
		add example of case where omitted variable is correlated
		tech discussion bias-variance

@@

		SM will deal with this.

>>>>

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We thank the reviewer for their comments and suggestions.
		}}
	\end{itemize}
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
			The reviewer raises an important connection to the spatial literature. The types of geographic dependencies in international relations are generally monadic in nature -- civil war spreads from Rwanda to Uganda, or protest from Lebanon to Syria. With dyadic data, however, we cannot use the common geographic adjacency matrices used for normal spatial econometrics, because in dyadic data a W matrix would need to specify how dyad i,j relates to dyad k,l (for every i,j,k,l). In the simulation, we do not include a spatial lag model because this would require specifying a spatial dependence pattern (see Plumper and Neumayer 2010 for a more in-depth discuss on spatial lags). \textbf{CD}: I added this as a footnote on p.9. I moved this footnote around a LOT but I think it needs to live somewhere in the simulation. It felt awkward within the text.
			}}
%		CDMG: Flag for discussion. We brainstormed how to fit this into the simulation, but wouldn't simulating a W matrix be a bit arbitrary here?
%		Reference papers that have thought about what happens when we get the wrong W
%		general gist .. spatial models of dyadic dvs are great if we know how to characterize the diffusion amtrices, but the point of our approach is that we may not know how to actually characterize the ways in which actors are related to one another on some diffusion space.
%		reference franzesse et al mstar framework as a way to operationalize multiple pathways of diffusion in a spatial econometric approach
	\end{itemize}
	\item It would help if the author discussed in more depth the properties of the AME estimator in the presence of unobserved dependencies. One would imagine that the oracle model, where all the unobserved factors and dependencies are accounted for should always outperform a parametric or semi-parametric estimator. Relatedly, it also would help to have a more technical discussion of the properties of AME models, particularly in terms of the bias-variance trade off.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		add example of case where omitted variable is correlated
		tech discussion bias-variance

		\begin{figure}[ht]
		\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
		\label{fig:ameBias}
		\includegraphics[width=1\textwidth]{ameSimBias_all_corrProbitMed.pdf} \\
		\end{figure}

		\begin{figure}[ht]
		\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
		\label{fig:ameBias}
		\includegraphics[width=1\textwidth]{ameSimBias_all_corrProbitHi.pdf} \\
		\end{figure}

		\begin{figure}[ht]
		\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
		\label{fig:ameBias}
		\includegraphics[width=1\textwidth]{ameSimBias_all_corrMed.pdf} \\
		\end{figure}

		\begin{figure}[ht]
		\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
		\label{fig:ameBias}
		\includegraphics[width=1\textwidth]{ameSimBias_all_corrHi.pdf} \\
		\end{figure}		

@@

		We've added additional discussion about how each of the variables in our simulation were generated. To make the model more applicable to the types of networks we study in IR we have provided a probit example.
